# Exam Questions

## SAS Questions

1.  Which of these CRAN packages can be used to import sas data files into R?

    A. haven

    B. sassy

    C. SAScii

    D. sass

    E. None of the above

    **Answer**: A. haven

2.  What is the extension of the standard sas data file?

    A. sas7bdat

    B. sas

    C. sasdat

    D. ss

    E. None of the above

    **Answer**: A. sas7bdat

3.  What does length denote for a character column in a SAS dataset?

    A. The maximum length any entry can be

    B. The length of that column

    C. The number of characters each entry is

    D. The number of bytes stored in each entry

    E. None of the above

    **Answer**: A. The maximum length any entry can be

4.  What is the extension of the open source SAS transport file?

    A. xpt

    B. sasxpf

    C. sas7xpt

    D. xpf

    E. All of the above

    **Answer**: A. xpt

5.  What formats exist in SAS by category?

    A. Character, DCBS, Numeric and 'Date and Time'

    B. String, DCBS, Double and 'Date and Time'

    C. Character, DCBS, Double and 'Date and Time'

    D. String, DCBS, Numeric and 'Date and Time'

    E. None of the above

    **Answer**: A. Character, DCBS, Numeric and 'Date and Time

6.  What is the purpose of the label attribute?

    A. A long form description of a column

    B. Notes on an output

    C. A long form description of a dataset

    D. A short form description of a dataset

    E. A short form description of a column

    **Answer**: A. A long form description of a column

7.  How does SAS indicate missing data in character vectors?

    A. An empty string

    B. NA

    C. NAC

    D. MISSING

    E. All of the above

    **Answer**: A. An empty string

8.  How does SAS indicate missing data in numeric vectors?

    A. .

    B. NA

    C. ;

    D. ,

    E. None of the above

    **Answer**: A. .

9.  What is the maximum length of SAS variable names?

    A. 32

    B. 16

    C. 8

    D. 64

    E. None of the above

    **Answer**: A. 32

10. What must the first letter of a SAS variable name be?

    A. A letter or an underscore

    B. A letter only

    C. A letter or a full stop

    D. A letter or a number

    E. None of the above

    **Answer**: A. A letter or an underscore

## CDISC/GCP Questions

1.  What is the main focus of Good Clinical Practices (GCP)?

    A. harmonized data collection

    B. standard analysis practices

    C. protection of subjects

    D. standard monitoring practices

    **Answer**: C. protection of subjects

2.  Specify the variable role which focus on the observation (such as the name of a lab test) of a SDTM data set?

    A. Identifier

    B. Topic

    C. Timing

    D. Qualifier

    **Answer**: B. Topic

3.  Concomitant/Prior Medications (CM) is a component of which SDTM class?

    A. Findings

    B. Interventions

    C. Events

    D. Special Purpose

    **Answer**: B. Interventions

4.  What is the primary purpose of programming validation?

    A. Ensure that the output from both the original program and the validation program match.

    B. Efficiently ensure any logic errors are discovered early in the programming process.

    C. Justify the means used to accomplish the outcome of a program and ensure its accurate representation of the original data.

    D. Document all specifications pertaining to programmed output and ensure all were reviewed during the programming process.

    **Answer**: C. Justify the means used to accomplish the outcome of a program and ensure its accurate representation of the original data.

5.  Why is the Demographics (DM) domain required for all human clinical trials regulatory submissions?

    A. It is a Findings domain that contains subject-related data not collected in other domains

    B. It is the parent domain for all other observations for human clinical subjects.

    C. It is a Findings domain that contains general subject characteristics about demography.

    D. It contains the actual order of elements followed by the subject.

    **Answer**: B. It is the parent domain for all other observations for human clinical subjects.

6.  Which statement is correct regarding Intention-to-Treat Population?

    A. Primary analysis should include all randomized subjects.

    B. Primary analysis should include all randomized subjects and a subject should take a single study drug.

    C. Primary analysis should include enrolled subjects.

    D. Primary analysis should include subjects who have taken at least a single study drug.

    **Answer**: A. Primary analysis should include all randomized subjects.

7.  Exposure data pertaining to body temperature associated with a fever should reside in which SDTMIG domain?

    A. Exposure (EX)

    B. Clinical Events (CE)

    C. Adverse Events (AE)

    D. Vital Signs (VS)

    **Answer**: D. Vital Signs (VS)

8.  Topic variable for the Interventions and Events General Observation Class model is often stored as \_\_\_\_\_\_\_.

    A. Standardized Value (AEDECOD, MHDECOD)

    B. Modified Value (CMMODIFY, PEMODIFY)

    C. Verbatim Value (AETERM, CMTRT)

    D. Original Value (AEORRES, MHORRES)

    **Answer**: C. Verbatim Value (AETERM, CMTRT)

9.  What is the maximum character limited allowed for ARMCD variable?

    A. 8 characters

    B. 20 characters

    C. 40 characters

    D. 200 characters

    **Answer**: B. 20 characters

10. Which date/time determines the population of the EPOCH variable if included in a general observation class domain?

    A. Start date/time of an observation or collection date/time

    B. Reference time point date/time

    C. Disease milestone instance date/time

    D. Planned start or end of assessment interval, as appropriate

    **Answer**: A. Start date/time of an observation or collection date/time.

## EDA Questions

1.  What package is used for creating data visualizations in R?

    A. dplyr

    B. ggplot2

    C. plotly

    D. cars

    E. B and C

    **Answer**: E. B and C

2.  Given the function below, what is the expected output of "final01"?

```{r, eval=FALSE}
final01 <- by(dataset, dataset$Drug, function(x){ calculation <- colMeans(x[,2:3])})
```

A. performs calculations of columns 2 and 3 and returns mean values(c)

B. provides the intercept of model -creates a separate dataset for EDA

C. takes the input of dataset and formats for reporting

D. performs a calculation on Drug column and stores in memory for later use

E. None of the above

**Answer**: A. performs calculations of columns 2 and 3 and returns mean values

3.  What function would be used in R to perform a t-test?

    A. t.test()

    B. t()

    C. T()

    D. T.Test()

    E. summarise()

    **Answer**: A. t.test()

4.  What does the summary() function perform in R?

    A. provides statistical summary of dataset

    B. generates a linear model

    C. assesses fit of linear model for all independent variables

    D. creates a summary plot of dependent variable

    E. assigns a variable summary to dataset for later use

    **Answer**: A. provides statistical summary of dataset

5.  What function is used to perform logorithmic scaling of data?

    A. log()

    B. logger()

    C. futilelog()

    D. caret()

    E. dplyr()

    **Answer**: A. log()

6.  What is the expected output of the code snippet below?

```{r, eval=FALSE}
ggplot(data = dataset, aes(x = x1, y = y1)) + geom_point() + stat_smooth(method = lm, col = "red")
```

A. linear model using x1 as independent variable and y1 as dependent variable

B. creates a scatter plot of x1 and y1

C. creates a line graph of x1 and y1

D. creates a line graph of x1 and y1 and adds confidence interval

E. creates a scatter plot of x1 and y1 and adds best fit line

**Answer**: E. creates a scatter plot of x1 and y1 and adds best fit line

7.  What does the pipe operator do in R (%\>%)?

    A. allows user to pass argument to another in sequence

    B. creates a new dataframe for analysis purposes

    C. creates a subset of a dataset

    D. defines a new user defined function for later use

    E. creates a data stream for real time data analysis

    **Answer**: A. allows user to pass argument to another in sequence

8.  What is does the str() function perform?

    A. shows internal structure of R objects

    B. shows all classes for individual dataset

    C. defines the type of input for all columns

    D. shows missing values of a dataframe

    E. type casts to a string object

    **Answer**: A. shows internal structure of R objects

9.  What package can be used for PCA (Principal Component Analysis)?

    A. cars

    B. tidyve

    C. ISLR

    D. psyh

    E. survival

    **Answer**: B. tidyverse

10. What function(s) can be used to identify the range of a numeric column in R?

    A. range()

    B. IQR()

    C. summary()

    D. all of the above

    E. both A and C

    **Answer**: E. both A and C

## Modeling Questions

1.  What package is used to reproduce SAS's predictions for linear modeling at combinations of specified factors?

    A. ANOVA

    B. lsmeans

    C. ISLR

    D. psych

    E. dplyr

    **Answer**: B. lsmeans

2.  Given the code snippet below, what is the expected value of "output"?

```{r, eval=FALSE}
output <- lm(PostTreatment ~ Drug + PreTreatment, data = anova)
```

A. ANOVA table of PostTreatment

B. Variance/Covariance Matrix of Drug and PreTreatment

C. Linear Model of PostTreatment as depdendent variable

D. Mixed-Effect model of PostTreatment as dependent variable

E. Residual analysis of anova dataset

**Answer**: C. Linear Model of PostTreatment as depdendent variable

3.  What package is used to perform survival analysis in R?

    A. psych

    B. dplyr

    C. sminer

    D. surry

    E. survival

    **Answer**: E. survival

4.  Given the linear mixed effect modeling function below, what is the fixed variable?

```{r, eval=FALSE}
melm <- lmer(AVAL ~ (1\|SITEGR1)+BASE+TRTPN,data=mlm_sub, REML = FALSE)
```

A. BASE

B. TRTPN

C. SITEGR1

D. AVAL

E. All variables not fixed

**Answer**: C. SITEGR1

5.  What is the expected output of the code snippet below?

```{r, eval=FALSE}
lung %>% filter(status == 2) %>% summarize(median_survival = median(time))
```

A. finds the median survial time for status == 2

B. group lung dataframe for status == 2

C. remove status == 2 from lung dataframe

D. provide summary statistics for lung dataframe where status==2

E. filter lung dataset to status==2 and determine median status for survival

**Answer**: A. finds the median survial time for status == 2

6.  What function would be used to pass a dataframe object (x) and output a covariance matrix?

    A. covariance(x)

    B. c.variance(x)

    C. covar(x)

    D. variance(x, type=covariance)

    E. cov(x)

    **Answer**: E. cov(x)

7.  Given the command below, what does the output produce?

```{r, eval=FALSE}
cor(df[,-1])
```

A. a correlation matrix excluding the first column

B. a correlation matrix excluding the last column

C. pearson's correlation of the last column

D. pearson's correlation of the first column

E. none of the above

**Answer**: A. a correlation matrix excluding the first column

8.  Given the code snippet below, what is the expected output?

```{r, eval=FALSE}
sapply(data,function(x)sum(is.na(x)))
```

A. sum the number of NAs in dataframe and output vector

B. replace all missing values with NA in data -impute missing values with 0 in dataframe

C. none of the above

D. sum the number of NAs in colun and output vector

E. none of the above

**Answer**: A. sum the number of NAs in dataframe and output vector

9.  What does the code snippet below perform?

```{r, eval=FALSE}
pnorm(q=-0.77, lower.tail=TRUE)
```

A. finds p-value with a z-score of -0.77 of left-tail test

B. finds p-value with a z-score of -0.77 of right-tail test

C. take the interquartile range of dataframe

D. creates normality test of a numeric vector

E. A or B

**Answer**: A. finds p-value with a z-score of -0.77 of left-tail test

10. To utilize survival package's modeling capabilities how must your dataset be passed as argument?

    A. as a tibble

    B. as a dataframe

    C. as either tibble or dataframe

    D. without missing data in any row

    E. none of the above

    **Answer**: C. as either tibble or dataframe

## Reporting Questions

1.  Which of these CRAN packages is used for Clinical Reporting Submissions to FDA?

    A. r2rtf

    B. exporter

    C. submissions

    D. reporting

    E. render

    **Answer**: A. r2rtf

2.  How would you pass an argument for fixing column width for tabular reporting?

    A. as a vector of argument

    B. line by line

    C. as a single fixed value for all columns

    D. reporting

    E. render

    **Answer**: A. as a vector of argument

3.  How are column headers passed an argument for tabular reporting?

    A. by a \| separator

    B. by a \*

    C. by a \_

    D. as a vector

    E. by the next capital character

    **Answer**: A. by a \| separator

4.  From the r2rtf package, what arguments are allowed for the function rtf_encode()

    A. tbl

    B. doc_type

    C. page_title

    D. verbose

    E. all of the above

    **Answer**: E. all of the above

5.  From the r2rtf package, what does the function justification() do?

    A. saves argument for alignment

    B. creates page breaks in reports

    C. aligns rows

    D. aligns texts

    E. C and D

    **Answer**: E. C and D

6.  What is the benefit of organizing a submission package with folder structures?

    A. Consistency

    B. Reproducibility

    C. Compliance

    D. Automation

    E. All of the above

    **Answer**: E. All of the above

7.  What data format is recommended for regulatory submissions by the FDA?

    A. .RData

    B. .xlm

    C. .csv

    D. .R

    E. All of the above

    **Answer**: A. .RData

8.  From the fmtr package, what is the purpose of the format catalog?

    A. save user defined formats for later use

    B. auto-generate formats

    C. create list of formats

    D. use SAS formats for reporting

    E. create user defined formats

    **Answer**: A. save user defined formats for later use

9.  Which of the following are not an output reporting format of reporter package?

    A. .txt

    B. .pdf

    C. .docx

    D. .rtf

    E. None of the above

    **Answer**: E. None of the above

10. Which logging package is part of the sassy meta-package?

    A. logr

    B. log4j

    C. logger

    D. futilelogger

    E. None of the above

    **Answer**: A. logr
